\chapter{server}
\label{chapter:server}

The design is that the server handles everything the clients are just
terminals which can send actions or receive actions. All games are stored on
the server, when a game is created it gets a numeric id, known as its token.
The games are stored on the server and keep running when all players
disconnected. They can also be stored on the disk of the server for later
retrieval. The GM can also allow who can download a game. A game has the
following properties:
\begin{description}
\item[id]
	A \mbox{$64$-bit} value which uniquely identifies a game on the server.
	This id can be changed when uploading a saved game.

\item[version]
	The version of the game data.

\item[name]
	The name of the game, this name needs to be unique on the server. It is
	the id players use to connect to a game.

\item[password]
	A password needed to manipulate the game.


\end{description}

game create, creates a new game, the player switches to the game and is M.

game save, saves the game on the local disk

game load, load a game from a local file to the server

game postpone, removes the game from the list of games in the lobby.

game retrieve, loads an postponed game into the list of games in the lobby

game close, the GM closes the game, no more actions can be done in the game

game open, reopens a closed game.

game join, joins a game in the lobby.

game delete, removes the game from the server and deletes its state on the
server. This action has no command to undo it, except when the game is
loaded again by a player.


notifications send by the server

player joined [NAME] a player joined the game or the lobby.

player left [NAME] a player went from game to lobby of vice versa

player disconnected [NAME] a player disconnected from the game or lobby



